---
title: "Multivariate Batch Effects"
author: "Eric Bridgeford"
date: "10/12/2020"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message=FALSE}
require(tidyverse)
require(grid)
require(MatchIt)
require(dplyr)
require(ggridges)
require(multcomp)
require(gridExtra)
require(parallel)
require(survey)
require(latex2exp)
require(energy)
require(gtable)
require(ggplotify)
require(kableExtra)
require(scales)
select <- dplyr::select; mutate <- dplyr::mutate; arrange=dplyr::arrange
```

# Modality {.tabset}

## fMRI {.tabset}

```{r}
results <- readRDS('../data/dcorr/pdcorr_outputs_fMRI_AAL.rds')


continent <- c("IBATRT"="North America", "Utah1"="North America", "IPCAS_2"="Asia", "SWU1"="Asia", "UWM"="North America", "XHCUMS"="Asia", "SWU4"="Asia",
               "BNU2"="Asia", "IPCAS_3"="Asia", "SWU3"="Asia", "IPCAS_4"="Asia", "NYU2"="North America", "IPCAS_1"="Asia",
               "IPCAS_7"="Asia", "UPSM_1"="North America", "IACAS_1"="Asia", "IPCAS_5"="Asia", "NYU_1"="North America", "NYU_2"="North America", "BNU1"="Asia",
               "MRN1"="North America", "BNU3"="Asia", "HNU1"="Asia", "SWU2"="Asia", "IPCAS_8"="Asia", "JHNU"="Asia", "IPCAS_6"="Asia",
               "BMB1"="Europe")
results$Covariate$Continent <- continent[results$Covariate$Dataset]

dset.ord <- results$Covariate %>%
  select(Dataset, Continent, n, N) %>%
  distinct() %>%
  arrange(Continent, n) %>%
  mutate(id=row_number()) %>%
  mutate(Dataset.Newname=sub("_", "", Dataset))

results$Site <- results$Site %>%
  left_join(dset.ord %>% select(Dataset, Dataset.Newname), by=c("Dataset.Trt"="Dataset")) %>%
  mutate(Dataset.Trt=Dataset.Newname) %>% select(-Dataset.Newname) %>%
  left_join(dset.ord %>% select(Dataset, Dataset.Newname), by=c("Dataset.Ctrl"="Dataset")) %>%
  mutate(Dataset.Ctrl=Dataset.Newname) %>% select(-Dataset.Newname)

results$Covariate <- results$Covariate %>%
  left_join(dset.ord %>% select(Dataset, Dataset.Newname), by=c("Dataset"="Dataset")) %>%
  mutate(Dataset=factor(Dataset.Newname, levels=dset.ord$Dataset.Newname, ordered=TRUE)) %>% select(-Dataset.Newname)

results$Signal <- results$Signal %>%
  left_join(dset.ord %>% select(Dataset, Dataset.Newname), by=c("Dataset"="Dataset")) %>%
  mutate(Dataset=factor(Dataset.Newname, levels=dset.ord$Dataset.Newname, ordered=TRUE)) %>% select(-Dataset.Newname)

dset.ord <- dset.ord %>%
  select(-Dataset) %>%
  rename(Dataset=Dataset.Newname)
```

### Site Effects {.tabset}

```{r}
results$Site <- results$Site %>%
  ungroup() %>%
  mutate(p.value=p.adjust(p.value, method="BH"),
         Dataset.Trt=factor(Dataset.Trt, 
                            levels=(dset.ord %>% arrange(n, rev(as.character(Dataset))))$Dataset, 
                            ordered=TRUE),
         Dataset.Ctrl=factor(Dataset.Ctrl, 
                             levels=(dset.ord %>% arrange(n, rev(as.character(Dataset))))$Dataset, 
                             ordered=TRUE))
```

```{r}
reverselog_trans <- function(base = exp(1)) {
    trans <- function(x) -log(x, base)
    inv <- function(x) base^(-x)
    trans_new(paste0("reverselog-", format(base)), trans, inv, 
              log_breaks(base = base), 
              domain = c(1e-100, Inf))
}

pval_hmap_chart <- function(data, title="", method="Raw", text.size=15, preproc=TRUE) {
  if (!preproc) {
    data <- data %>%
      mutate(Data=recode_factor(Data, "Untrimmed"="Associational", "Trimmed"="Propensity-Trimmed")) %>%
      filter(Method == method) %>%
      left_join((.) %>% filter(Data == "Propensity-Trimmed") %>% 
                  select(Dataset.Ctrl, Dataset.Trt, Method) %>% mutate(is.good=TRUE),
                by=c("Dataset.Ctrl", "Dataset.Trt", "Method")) %>%
      mutate(is.good=ifelse(is.na(is.good), FALSE, TRUE))
  }
  data <- data %>%
    mutate(Dataset.tmp = as.character(Dataset.Trt),
           Dataset.Trt=ifelse(Data == "Propensity-Trimmed", as.character(Dataset.Ctrl), as.character(Dataset.Trt)),
           Dataset.Ctrl=ifelse(Data == "Propensity-Trimmed", as.character(Dataset.tmp), as.character(Dataset.Ctrl)),
           Dataset.Trt=factor(Dataset.Trt, 
                              levels=(dset.ord %>% arrange(n, rev(as.character(Dataset))))$Dataset, 
                              ordered=TRUE),
           Dataset.Ctrl=factor(Dataset.Ctrl, 
                               levels=(dset.ord %>% arrange(n, rev(as.character(Dataset))))$Dataset, 
                               ordered=TRUE)) %>%
    select(-Dataset.tmp)
  data %>%
    ggplot(aes(x=Dataset.Trt, y=Dataset.Ctrl, fill=Data, alpha=p.value)) +
    geom_tile() +
    xlab("Control Dataset") +
    ylab("Treatment Dataset") +
    scale_alpha_continuous(trans=reverselog_trans(10), limits=c(1, .009), breaks=c(.01, .1, 1), name="p-value") +
    scale_fill_manual(values=c("Propensity-Trimmed"="dark green", "Associational"="red"), name="Estimated Effect") +
    ggtitle(title) +
    theme_bw() +
    theme(text=element_text(size=text.size), axis.text.x=element_text(angle=90),
          panel.grid.major=element_blank(),
          panel.grid.minor = element_blank())
}


pval_hist_chart <- function(data, nbreaks=30, title="", y.scale=.03, text.y=.4, method="Raw",
                            text.size=15, preproc=TRUE, p.adjust=.0005) {
  if (!preproc) {
    data <- data %>%
      mutate(Data=recode_factor(Data, "Untrimmed"="Associational", "Trimmed"="Propensity-Trimmed")) %>%
      filter(Method == method) %>%
      left_join((.) %>% filter(Data == "Propensity-Trimmed") %>% 
                  select(Dataset.Ctrl, Dataset.Trt, Method) %>% mutate(is.good=TRUE),
                by=c("Dataset.Ctrl", "Dataset.Trt", "Method")) %>%
      mutate(is.good=ifelse(is.na(is.good), FALSE, TRUE))
  }
  pval.breaks <- seq(0, 1, length.out=nbreaks)
  
  sum.n <- data %>%
    group_by(Data, Method) %>%
    summarize(count=n()) %>%
    mutate(text=sprintf("n=%d", count)) %>%
    ungroup() %>%
    select(Data, text)
  
  data.rand <- data %>% sample_n(nrow(.))
  plt <- data %>%
    arrange(Data) %>%
    ggplot() +
      geom_histogram(aes(p.value, color=Data, fill=Data,
                         group=paste0(Data, Method),
                         y=..count../tapply(..count.., ..group.., sum)[..group..]),
                     alpha=.5, position="dodge") +
      geom_jitter(data=data.rand, 
                  aes(p.value+p.adjust, group=paste0(Data, Method), y=-3/2*y.scale, fill=Data,
                      color=Data), width=30*ggplot2:::resolution(log10(data.rand$p.value), FALSE),
                  height=y.scale, size=.02) +
      facet_grid(".~Data") +
      geom_text(data=data.frame(x=.05, y=text.y/2, Data="Associational", text="$\\alpha$=.05"),
              aes(x=x, y=y, label=TeX(text, output="character")), 
              nudge_x=.2, color='black', parse=TRUE) +
      geom_text(data=sum.n, aes(x=1, y=text.y, label=text), color='black', nudge_x=-.15) +
      scale_fill_manual(values=c("Associational"="red", "Propensity-Trimmed"="darkgreen"), name="Estimated Effect") +
      scale_color_manual(values=c("Associational"="red", "Propensity-Trimmed"="darkgreen")) +
      scale_x_continuous(expand=c(0, 0), limits=c(.009, 1), breaks=c(.01, .1, 1), trans="log10") +
      scale_y_continuous(expand=c(0, 0.03), limits=c(-.25, 1), breaks=c(0, .5, 1)) +
      xlab("p-value") +
      ylab("Fraction of p-values") +
      ggtitle(title) +
      theme_bw() +
      theme(text=element_text(size=text.size)) +
      geom_vline(xintercept = .05, linetype="dashed") +
      guides(fill=FALSE, shape=FALSE, color=FALSE)
  return(as.ggplot(gtable_filter(ggplotGrob(plt), "axis-b-2", trim=FALSE, invert=TRUE)))
}

compare_site <- function(data, method="Raw", nbreaks=30, text.y=.4, y.scale=.03, title.hmap="",
                         title.hist="", text.size=15, p.adjust=0) {
  data <- data %>%
    mutate(Data=recode_factor(Data, "Untrimmed"="Associational", "Trimmed"="Propensity-Trimmed")) %>%
    filter(Method == method) %>%
    left_join((.) %>% filter(Data == "Propensity-Trimmed") %>% 
                select(Dataset.Ctrl, Dataset.Trt, Method) %>% mutate(is.good=TRUE),
              by=c("Dataset.Ctrl", "Dataset.Trt", "Method")) %>%
    mutate(is.good=ifelse(is.na(is.good), FALSE, TRUE))
  
  p.hmap <- pval_hmap_chart(data, method=method, title=title.hmap, text.size=text.size)
  p.hist <- pval_hist_chart(data, method=method, nbreaks=nbreaks, title=title.hist,
                            y.scale=y.scale, text.y=text.y, text.size=text.size, p.adjust=p.adjust)
  arrangeGrob(p.hmap, p.hist, heights=c(.7, .3), nrow=2)
}
```

```{r, warning=FALSE, message=FALSE}
params <- list(Raw=list(method="Raw", title.hmap="Detectability of Site-Related Effect Before Site Correction", p.adjust=.0005),
               ComBat=list(method="ComBat", title.hmap="Detectability of Site-Related Effect After ComBat", p.adjust=0),
               Ranked=list(method="Ranked", title.hmap="Detetectability of Site-Related Effect After Ranking", p.adjust=0),
               ZScore=list(method="Z-Score", title.hmap="Detectability of Site-Related Effect After Z-Scoring", p.adjust=0))

plts <- lapply(params, function(param) {
  compare_site(results$Site, method=param$method, text.y=.8, y.scale=.1, title.hmap=param$title.hmap, p.adjust=param$p.adjust)
})
names(plts) <- names(plts)
```

#### Raw

```{r, fig.height=9, fig.width=8, warning=FALSE, message=FALSE}
plot(plts$Raw)
```

#### ComBat

```{r, fig.height=9, fig.width=8, warning=FALSE, message=FALSE}
plot(plts$ComBat)
```

#### Ranked

```{r, fig.height=9, fig.width=8, warning=FALSE, message=FALSE}
plot(plts$Ranked)
```

#### Z-Score

```{r, fig.height=9, fig.width=8, warning=FALSE, message=FALSE}
plot(plts$ZScore)
```

### Between-Individual Covariate Effects

```{r}
results$Covariate <- results$Covariate %>%
  ungroup() %>%
  mutate(p.value=p.adjust(p.value, method="BH")) %>%
  filter(Variance > 0)
```

```{r}
tab.cov <- results$Covariate %>%
  group_by(Method, Effect.Name) %>%
  summarize(Sig=sum(p.value <= .05), N.Tests=n()) %>%
  mutate(Significant=sprintf("%d/%d", Sig, N.Tests)) %>%
  select(-c("Sig", "N.Tests")) %>%
  rename("Effect"=Effect.Name) %>%
  pivot_wider(Method, names_from="Effect", values_from="Significant") %>%
  select(Method, Sex, Age) %>%
  mutate(Method=factor(Method, levels=c("Raw", "ComBat", "Ranked", "Z-Score"),
                       ordered=TRUE)) %>%
  arrange(Method)
```

```{r}
tab.cov %>%
  kbl() %>%
  kable_paper("hover")
```


#### Forest Plot

```{r, fig.height=1.75, fig.width=13, message=FALSE, warning=FALSE}
tab.cov %>%
  pivot_longer(Sex:Age, names_to="Effect.Name", values_to="Total") %>%
  ggplot(aes(x=0, y="# Significant")) +
  geom_tile(fill="white") +
  geom_text(aes(label=Total), size=12) +
  facet_nested(.~Effect.Name + Method) +
  scale_x_continuous(breaks=c(), name="") +
  scale_y_discrete(name="") +
  theme_bw() +
  theme(text=element_text(size=15), panel.spacing=unit(0,"lines"))
```

```{r, fig.height=7, fig.width=14, message=FALSE, warning=FALSE}
# plt.forest <- results$Covariate %>%
#   filter(Method %in% c("Raw", "ComBat")) %>%
#   mutate(Significant=ifelse(p.value <= .05, "Yes", "No"),
#          Method=factor(Method, levels=c("Raw", "ComBat"), ordered=TRUE),#, "Ranked", "Z-Score"), ordered=TRUE),
#          Dataset=factor(Dataset, levels=dset.ord$Dataset, ordered=TRUE),
#          ypos= (as.numeric(Dataset) + (as.numeric(Method) - 1.5)/2)) %>%
#   ggplot(aes(x=Effect, shape=Method, xmin=Effect.lwr.jk, xmax=Effect.upr.jk, y=ypos, 
#              color=Significant)) +
#     geom_pointrange() +
#     facet_grid(".~Effect.Name") +
#     geom_vline(aes(xintercept=0), color="black", linetype="dashed") +
#     scale_color_manual(values=c("No"="red", "Yes"="darkgreen"), name="Reject Null") +
#     scale_y_continuous(labels=dset.ord$Dataset, breaks=dset.ord$id,
#                        limits=c(min(dset.ord$id) - .5, max(dset.ord$id) + .5), expand=c(0,0),
#                        name="Dataset") +
#     theme_bw() +
#     ggtitle("Forest Plot of Demographic Effects") +
#     theme(text=element_text(size=15))
plt.forest <- results$Covariate %>%
  mutate(Significant=ifelse(p.value <= .05, "Yes", "No"),
         Method=factor(Method, levels=c("Raw", "ComBat", "Ranked", "Z-Score"), ordered=TRUE),
         Dataset=factor(Dataset, levels=dset.ord$Dataset, ordered=TRUE)) %>%
  ggplot(aes(x=Effect, xmin=Effect.lwr.jk, xmax=Effect.upr.jk, y=Dataset, 
             color=Significant)) +
    geom_pointrange() +
    facet_nested(.~Effect.Name + Method) +
    geom_vline(aes(xintercept=0), color="black", linetype="dashed") +
    scale_color_manual(values=c("No"="red", "Yes"="darkgreen"), name="Significant") +
    theme_bw() +
    ggtitle("Forest Plot of Demographic Effects") +
    theme(text=element_text(size=15), panel.spacing=unit(0,"lines")) +
    scale_x_continuous(limits = c(-.2, .2), breaks=c(-.2, 0, .2))

as.ggplot(gtable_filter(ggplotGrob(plt.forest), "axis-b-[2,3,4,5,6,7,8]", trim=FALSE, invert=TRUE))
```

```{r}
tab.plt <- tab.cov %>%
  pivot_longer("Sex":"Age", names_to="Demographic", values_to="Value") %>%
  ggplot(aes(x=Demographic, y=Method)) +
  geom_tile(fill="white") +
  geom_text(aes(label=Value), size=5) +
  facet_grid("Method~Demographic", scales="free", switch="y") +
  scale_x_discrete(expand=c(0,0), breaks=NaN, position="top", name="Demographic Characteristic") +
  scale_y_discrete(expand=c(0,0), breaks=NaN, name="Normalization Strategy") +
  theme_bw() +
  ggtitle("(B) Fraction of Within-Site Demographic Effects Detected") +
  theme(text=element_text(size=15), panel.spacing=unit(0, "lines"),
        strip.text.y.left=element_text(angle=0))

plot(tab.plt)
```

```{r, fig.height=10, fig.width=8}
grid.arrange(plt.forest, tab.plt, heights=c(.7, .3))
```

#### Effects WRT Variability in the Data {.tabset}

##### Sex

```{r}
results$Covariate %>%
  filter(Effect.Name == "Sex") %>%
  pivot_longer(c("Entropy", "Variance"), names_to="Measure", values_to="Value") %>%
  ggplot(aes(x=Value, y=Effect, color=Dataset)) +
    geom_point() +
    facet_grid("Method~Measure", scales="free_x") +
    ylab("Sex Effect") +
    ggtitle("Sex Effect vs Notions of Variability in Sex Demographic") +
    theme_bw()
```

##### Age

```{r}
results$Covariate %>%
  filter(Effect.Name == "Age") %>%
  pivot_longer(c("Entropy", "Variance"), names_to="Measure", values_to="Value") %>%
  ggplot(aes(x=Value, y=Effect, color=Dataset)) +
    geom_point() +
    facet_grid("Method~Measure", scales="free_x") +
    ylab("Age Effect") +
    ggtitle("Age Effect vs Notions of Variability in Age Demographic") +
    theme_bw()
```

### Looking at Signal Preservation

```{r, fig.width=9, fig.height=4}
plt <- results$Signal %>%
  mutate(Measure=recode_factor(Community, "Homophilic"="Homophilic Difference", "Homotopic"="Homotopic Difference"),
         Method=factor(Method, ordered=TRUE, levels=c("Raw", "ComBat", "Z-Score", "Ranked")),
         p.value=p.adjust(p.value, method="BH")) %>%
  ggplot(aes(p.value, color=Method)) +
  stat_ecdf(aes(linetype=Method), geom="step", size=1.02) +
    facet_grid(". ~ Measure") +
    scale_color_manual(values = c("Raw"="chartreuse4", "ComBat"="blue", "Z-Score"="red", "Ranked"="darkred")) +
    scale_linetype_manual(values = c("Raw"="solid", "ComBat"="dashed", "Z-Score"="solid", "Ranked"="solid")) +
    xlab("p-value") +
    scale_x_continuous(limits=c(0, 1), expand=c(0.005,0.005)) +
    scale_y_continuous(limits=c(0, 1), expand=c(0,0)) +
    ylab("Cumulative Distribution") +
    geom_vline(xintercept = .05, size=1.02, linetype='dashed') +
    theme_bw() +
    ggtitle("Preservation of Within-Individual Signal by Normalization Technique") +
    geom_text(data=data.frame(x=.05, y=.8,Measure="Homophilic Difference", text="$\\alpha$=.05"),
            aes(x=x, y=y, label=TeX(text, output="character")), 
            nudge_x=.2, color='black', parse=TRUE) +
    theme(text=element_text(size=15))
as.ggplot(gtable_filter(ggplotGrob(plt), "axis-b-2", trim=FALSE, invert=TRUE))
```


## dMRI {.tabset}

```{r}
results <- readRDS('../data/dcorr/pdcorr_outputs_dMRI_AAL.rds')


continent <- c("IBATRT"="North America", "Utah1"="North America", "IPCAS_2"="Asia", "SWU1"="Asia", "UWM"="North America", "XHCUMS"="Asia", "SWU4"="Asia",
               "BNU2"="Asia", "IPCAS_3"="Asia", "SWU3"="Asia", "IPCAS_4"="Asia", "NYU2"="North America", "IPCAS_1"="Asia",
               "IPCAS_7"="Asia", "UPSM_1"="North America", "IACAS_1"="Asia", "IPCAS_5"="Asia", "NYU_1"="North America", "NYU_2"="North America", "BNU1"="Asia",
               "MRN1"="North America", "BNU3"="Asia", "HNU1"="Asia", "SWU2"="Asia", "IPCAS_8"="Asia", "JHNU"="Asia", "IPCAS_6"="Asia",
               "BMB1"="Europe")
results$Covariate$Continent <- continent[results$Covariate$Dataset]

dset.ord <- results$Covariate %>%
  select(Dataset, Continent, n, N) %>%
  distinct() %>%
  arrange(Continent, n) %>%
  mutate(id=row_number()) %>%
  mutate(Dataset.Newname=sub("_", "", Dataset))

results$Site <- results$Site %>%
  left_join(dset.ord %>% select(Dataset, Dataset.Newname), by=c("Dataset.Trt"="Dataset")) %>%
  mutate(Dataset.Trt=Dataset.Newname) %>% select(-Dataset.Newname) %>%
  left_join(dset.ord %>% select(Dataset, Dataset.Newname), by=c("Dataset.Ctrl"="Dataset")) %>%
  mutate(Dataset.Ctrl=Dataset.Newname) %>% select(-Dataset.Newname)

results$Covariate <- results$Covariate %>%
  left_join(dset.ord %>% select(Dataset, Dataset.Newname), by=c("Dataset"="Dataset")) %>%
  mutate(Dataset=factor(Dataset.Newname, levels=dset.ord$Dataset.Newname, ordered=TRUE)) %>% select(-Dataset.Newname)

results$Signal <- results$Signal %>%
  left_join(dset.ord %>% select(Dataset, Dataset.Newname), by=c("Dataset"="Dataset")) %>%
  mutate(Dataset=factor(Dataset.Newname, levels=dset.ord$Dataset.Newname, ordered=TRUE)) %>% select(-Dataset.Newname)

dset.ord <- dset.ord %>%
  select(-Dataset) %>%
  rename(Dataset=Dataset.Newname)
```

### Site Effects {.tabset}

```{r}
results$Site <- results$Site %>%
  ungroup() %>%
  mutate(p.value=p.adjust(p.value, method="BH"),
         Dataset.Trt=factor(Dataset.Trt, 
                            levels=(dset.ord %>% arrange(n, rev(as.character(Dataset))))$Dataset, 
                            ordered=TRUE),
         Dataset.Ctrl=factor(Dataset.Ctrl, 
                             levels=(dset.ord %>% arrange(n, rev(as.character(Dataset))))$Dataset, 
                             ordered=TRUE))
```

```{r, warning=FALSE, message=FALSE}
params <- list(Raw=list(method="Raw", title.hmap="Detectability of Site-Related Effect Before Site Correction"),
               ComBat=list(method="ComBat", title.hmap="Detectability of Site-Related Effect After ComBat"),
               Ranked=list(method="Ranked", title.hmap="Detetectability of Site-Related Effect After Ranking"),
               ZScore=list(method="Z-Score", title.hmap="Detectability of Site-Related Effect After Z-Scoring"))

plts <- lapply(params, function(param) {
  pval_hmap_chart(results$Site, method=param$method, title=param$title.hmap, preproc=FALSE)
})
names(plts) <- names(plts)
```

#### Raw

```{r, fig.height=5, fig.width=7, warning=FALSE, message=FALSE}
plot(plts$Raw)
```


#### ComBat

```{r, fig.height=5, fig.width=7, warning=FALSE, message=FALSE}
plot(plts$ComBat)
```

#### Ranked

```{r, fig.height=5, fig.width=7, warning=FALSE, message=FALSE}
plot(plts$Ranked)
```

#### Z-Score

```{r, fig.height=5, fig.width=7, warning=FALSE, message=FALSE}
plot(plts$ZScore)
```

### Between-Individual Covariate Effects {.tabset}

```{r}
results$Covariate <- results$Covariate %>%
  ungroup() %>%
  mutate(p.value=p.adjust(p.value, method="BH")) %>%
  filter(Variance > 0)
```

```{r}
tab.cov <- results$Covariate %>%
  group_by(Method, Effect.Name) %>%
  summarize(Sig=sum(p.value <= .05), N.Tests=n()) %>%
  mutate(Significant=sprintf("%d/%d", Sig, N.Tests)) %>%
  select(-c("Sig", "N.Tests")) %>%
  rename("Effect"=Effect.Name) %>%
  pivot_wider(Method, names_from="Effect", values_from="Significant") %>%
  select(Method, Sex, Age) %>%
  mutate(Method=factor(Method, levels=c("Raw", "ComBat", "Ranked", "Z-Score"),
                       ordered=TRUE)) %>%
  arrange(Method)
```

```{r}
tab.cov %>%
  kbl() %>%
  kable_paper("hover")
```


#### Forest Plot

```{r, fig.height=8, fig.width=6}
results$Covariate %>%
  mutate(Significant=ifelse(p.value <= .05, "Yes", "No"),
         Method=factor(Method, levels=c("Raw", "ComBat", "Ranked", "Z-Score"), ordered=TRUE),
         Dataset=factor(Dataset, levels=dset.ord$Dataset, ordered=TRUE),
         ypos= (as.numeric(Dataset) + (as.numeric(Method) - 2)/6)) %>%
  ggplot(aes(x=Effect, shape=Method, xmin=Effect.lwr.jk, xmax=Effect.upr.jk, y=ypos, 
             color=Significant)) +
    geom_pointrange() +
    facet_grid(".~Effect.Name") +
    geom_vline(aes(xintercept=0), color="black", linetype="dashed") +
    scale_color_manual(values=c("No"="red", "Yes"="darkgreen"), name="Significant") +
    scale_y_continuous(labels=dset.ord$Dataset, breaks=dset.ord$id,
                       limits=c(min(dset.ord$id) - .5, max(dset.ord$id) + .5), expand=c(0,0),
                       name="Dataset") +
    theme_bw() +
    ggtitle("Forest Plot")
```


#### Effects WRT Variability in the Data {.tabset}

##### Sex

```{r}
results$Covariate %>%
  filter(Effect.Name == "Sex") %>%
  pivot_longer(c("Entropy", "Variance"), names_to="Measure", values_to="Value") %>%
  ggplot(aes(x=Value, y=Effect, color=Dataset)) +
    geom_point() +
    facet_grid("Method~Measure", scales="free_x") +
    ylab("Sex Effect") +
    ggtitle("Sex Effect vs Notions of Variability in Sex Demographic") +
    theme_bw()
```

##### Age

```{r}
results$Covariate %>%
  filter(Effect.Name == "Age") %>%
  pivot_longer(c("Entropy", "Variance"), names_to="Measure", values_to="Value") %>%
  ggplot(aes(x=Value, y=Effect, color=Dataset)) +
    geom_point() +
    facet_grid("Method~Measure", scales="free_x") +
    ylab("Age Effect") +
    ggtitle("Age Effect vs Notions of Variability in Age Demographic") +
    theme_bw()
```

### Looking at Signal Preservation

```{r, fig.width=6, fig.height=3}
plt <- results$Signal %>%
  mutate(Measure=recode_factor(Community, "Homophilic"="Homophilic Difference", "Homotopic"="Homotopic Difference"),
         Method=factor(Method, ordered=TRUE, levels=c("Raw", "ComBat", "Z-Score", "Ranked"))) %>%
  ggplot(aes(p.value, color=Method)) +
  stat_ecdf(geom="step") +
    facet_grid(". ~ Measure") +
    scale_color_manual(values = c("Raw"="green", "ComBat"="darkgreen", "Z-Score"="red", "Ranked"="darkred")) +
    xlab("p-value") +
    ylab("ecdf of p-values") +
    geom_vline(xintercept = .05, linetype='dashed') +
    theme_bw() +
    ggtitle("Preservation of Signal Effect by Correction Technique") +
    geom_text(data=data.frame(x=.05, y=.8,Measure="Homophilic Difference", text="$\\alpha$=.05"),
            aes(x=x, y=y, label=TeX(text, output="character")), 
            nudge_x=.2, color='black', parse=TRUE)
as.ggplot(gtable_filter(ggplotGrob(plt), "axis-b-2", trim=FALSE, invert=TRUE))
```
