---
title: "Multivariate Batch Effects"
author: "Eric Bridgeford"
date: "10/12/2020"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message=FALSE}
require(tidyverse)
require(grid)
require(dplyr)
require(ggridges)
require(multcomp)
require(gridExtra)
require(parallel)
require(survey)
require(latex2exp)
require(energy)
require(gtable)
require(ggplotify)
require(kableExtra)
require(scales)
require(ggh4x)
require(cowplot)
source('./causal_investigation_helpers.R')
select <- dplyr::select; mutate <- dplyr::mutate; arrange=dplyr::arrange
```

# Modality {.tabset}

## fMRI {.tabset}

```{r}
results <- readRDS('../data/dcorr/pdcorr_outputs_fMRI_AAL.rds')

continent <- c("IBATRT"="North America", "Utah1"="North America", "IPCAS2"="Asia",
               "SWU1"="Asia", "UWM"="North America", "XHCUMS"="Asia", "SWU4"="Asia",
               "BNU2"="Asia", "IPCAS3"="Asia", "SWU3"="Asia", "IPCAS4"="Asia",
               "NYU2"="North America", "IPCAS1"="Asia",
               "IPCAS7"="Asia", "UPSM1"="North America", "IACAS1"="Asia", "IPCAS5"="Asia", 
               "NYU1"="North America", "NYU2"="North America", "BNU1"="Asia",
               "MRN1"="North America", "BNU3"="Asia", "HNU1"="Asia", "SWU2"="Asia",
               "IPCAS8"="Asia", "JHNU"="Asia", "IPCAS6"="Asia",
               "BMB1"="Europe", "NKI24tr645"="North America", 
               "NKI24tr1400"="North America", "NKI24tr2500"="North America")
results$Covariate$Continent <- continent[results$Covariate$Dataset]

dset.ord <- results$Covariate %>%
  filter(Method == "Raw") %>%
  select(Dataset, Continent, n, N) %>%
  distinct() %>%
  arrange(Continent, N) %>%
  mutate(id=row_number()) %>%
  mutate(Dataset.Newname=sub("_", "", Dataset))
```

### Exploratory

```{r, fig.height=12, fig.width=9}
get_scaled_densities <- function(x, bw=1.58) {
  res <- density(x, bw=bw)
  return(data.frame(x=res$x, y=res$y/max(res$y)*length(x)))
}
covar.reord <- results$Covar.Tbl %>%
  filter(!(Dataset %in% c("NKI24tr645", "NKI24tr1400"))) %>%
  mutate(Dataset=recode_factor(Dataset, "NKI24tr2500"="NKI24")) %>%
  mutate(Dataset=factor(Dataset, levels=(dset.ord %>%
  filter(!(Dataset %in% c("NKI24tr645", "NKI24tr1400"))) %>%
  mutate(Dataset=recode_factor(Dataset, "NKI24tr2500"="NKI24")))$Dataset, ordered=TRUE)) %>%
  group_by(Subid, Dataset) %>%
  arrange(desc(Session)) %>%
  do(head(., 1))

plt <- (df <- covar.reord %>%
  group_by(Dataset, Sex, Continent) %>%
  do(get_scaled_densities(.$Age)) %>%
  ungroup() %>%
  mutate(y=y/max(y) + as.numeric(Dataset))) %>%
  ggplot(aes(ymin=as.numeric(Dataset), group=paste0(Dataset, Sex),
             color=factor(Sex), fill=factor(Sex), x=x, y=y, ymax=y)) +
    geom_ribbon(alpha=.2) +
    geom_line(color='black') +
    geom_jitter(data=covar.reord,
                aes(x=Age, y=as.numeric(Dataset), color=factor(Sex)), width=.25, height=.2, size=.1, inherit.aes = FALSE) +
    scale_fill_manual(values=c(`1`="red", `2`="blue"), labels=c(`1`="Female", `2`="Male"), name="Sex") +
    scale_color_manual(values=c(`1`="red", `2`="blue"), labels=c(`1`="Female", `2`="Male"), name="Sex", aesthetics="color") +
    scale_y_continuous(breaks=1:length(levels(df$Dataset)),
                       labels=levels(df$Dataset), name="Dataset", expand=c(.02,.02), position="right") +
    xlab("Age") +
    theme_bw(base_size = 20) +
    facet_grid("Continent~.", scales="free_y", space="free_y", switch="y") +
    theme(panel.grid.minor = element_blank())

plt = plt %>%
  grid.arrange(left=ggpubr::text_grob("Continent",size=25, rot=90))

plt

```

```{r, fig.width=8.5, fig.height=2.5}
graph2df <- function(gr) {
  rownames(gr) <- 1:dim(gr)[1]
  colnames(gr) <- 1:dim(gr)[2]
  data.frame(gr) %>%
    mutate(Row=row_number()) %>%
    pivot_longer("X1":sprintf("X%d", dim(gr)[2]), names_to="Column", values_to="Value") %>%
    mutate(Column=gsub("X", "", Column), Column=factor(Column, levels=colnames(gr), ordered=TRUE),
           Row=factor(Row, levels=rownames(gr), ordered=TRUE),
           Col.mod2=as.numeric(Column) %% 2, Row.mod2=as.numeric(Row) %% 2)
}
get_connectomes_dataset <- function(data, dataset="BNU1") {
  rbind(graph2df(data$Raw$Dataset[[dataset]]$Male.Young) %>% mutate(Vara="Male, Young", Dataset=dataset),
        graph2df(data$Raw$Dataset[[dataset]]$Male.Old) %>% mutate(Vara="Male, Old", Dataset=dataset),
        graph2df(data$Raw$Dataset[[dataset]]$Female.Young) %>% mutate(Vara="Female, Young", Dataset=dataset),
        graph2df(data$Raw$Dataset[[dataset]]$Female.Old) %>% mutate(Vara="Female, Old", Dataset=dataset))
}

rbind(#get_connectomes_dataset(results$Stats, dataset="BNU1"),
      #get_connectomes_dataset(results$Stats, dataset="HNU1"),
      get_connectomes_dataset(results$Stats, dataset="NYU2")) %>%
  ggplot(aes(x=reorder(Row, Row.mod2), y=reorder(Column, Col.mod2), fill=Value)) +
    geom_tile() +
    # facet_grid(Dataset ~ Vara) +
    facet_grid(.~Vara) +
    scale_x_discrete(breaks=c(), name="Parcel") +
    scale_y_discrete(breaks=c(), name="Parcel") +
    theme_bw() +
    scale_fill_gradient(high="#530481", low="#fdf2fe", name="Weight", breaks=c(0, .5, 1), limits=c(0, 1)) +
    ggtitle("Raw fMRI Connectomes from NYU2 Study") +
    theme(text=element_text(size=15))
```

810x500 px


### Site Effects {.tabset}

```{r}
dset.ord.site <- dset.ord %>%
  arrange(Continent, n, rev(as.character(Dataset))) %>%
  ungroup() %>% mutate(id=row_number())

results$Site <- results$Site %>%
  ungroup() %>%
  mutate(p.value=p.adjust(p.value, method="BH"),
         Dataset.Trt=factor(Dataset.Trt, 
                            levels=dset.ord.site$Dataset, 
                            ordered=TRUE),
         Dataset.Ctrl=factor(Dataset.Ctrl, 
                             levels=dset.ord.site$Dataset, 
                             ordered=TRUE)) %>%
  mutate(Data=factor(Data, levels=c("Associational", "Conditional", "Adjusted", "Causal Cross."), ordered=TRUE))
  
```

```{r}
reverselog_trans <- function(base = exp(1)) {
    trans <- function(x) -log(x, base)
    inv <- function(x) base^(-x)
    trans_new(paste0("reverselog-", format(base)), trans, inv, 
              log_breaks(base = base), 
              domain = c(1e-100, Inf))
}
pval_hmap_chart <- function(data, dset.ord.site, title="", alpha=.05, method="Raw", text.size=15, preproc=TRUE) {
  if (!preproc) {
    data <- data %>%
      filter(Method == method) %>%
      left_join((.) %>% filter(grepl("Causal", Data)) %>% 
                  select(Dataset.Ctrl, Dataset.Trt, Method) %>% mutate(has.causal=TRUE),
                by=c("Dataset.Ctrl", "Dataset.Trt", "Method")) %>%
      mutate(has.causal=ifelse(is.na(has.causal), FALSE, TRUE))
  }
  
  dset.ord.trt <- dset.ord.site %>%
     rename(n.trt=n, Dataset.Trt= Dataset, id.trt=id) %>%
     select(n.trt, Dataset.Trt, id.trt)
  dset.ord.ctrl <- dset.ord.site %>%
     rename(n.ctrl=n, Dataset.Ctrl= Dataset, id.ctrl=id) %>%
     select(n.ctrl, Dataset.Ctrl, id.ctrl)
  # data <- data %>% filter(Data %in% c("Adjusted", "Causal Cross.", "Associational")) %>%
  #   filter(!(Data == "Adjusted" & grepl("NKI", Dataset.Trt) & grepl("NKI", Dataset.Ctrl)))
  data.caus <- data %>%
    filter(Data %in% c("Causal Cross.", "Adjusted")) %>%
    left_join(dset.ord.trt) %>%
    left_join(dset.ord.ctrl) %>%
    ungroup() %>%
    mutate(id.row=row_number()) %>%
    group_by(id.row) %>%
    mutate(Dataset.Trt.X=c(Dataset.Trt, Dataset.Ctrl)[which.min(c(id.trt, id.ctrl))],
           Dataset.Ctrl.X=c(Dataset.Trt, Dataset.Ctrl)[which.max(c(id.trt, id.ctrl))],
           Dataset.Trt=Dataset.Trt.X, Dataset.Ctrl=Dataset.Ctrl.X,
           Dataset.tmp=as.character(Dataset.Trt),
           Dataset.Trt=ifelse(grepl("Causal Cross.", Data), as.character(Dataset.Ctrl), as.character(Dataset.Trt)),
           Dataset.Ctrl=ifelse(grepl("Causal Cross.", Data), as.character(Dataset.tmp), as.character(Dataset.Ctrl)),
           Dataset.Trt=factor(Dataset.Trt,
                              levels=dset.ord.site$Dataset,
                              ordered=TRUE),
           Dataset.Ctrl=factor(Dataset.Ctrl,
                               levels=dset.ord.site$Dataset,
                               ordered=TRUE))
  
  sig.dat <- data.caus %>% filter(p.value < alpha)
  
  empty.df <- expand.grid(dset.ord.trt$Dataset.Trt, dset.ord.trt$Dataset.Trt) %>%
    rename(Dataset.Trt=Var1, Dataset.Ctrl=Var2) %>%
    filter(!(Dataset.Trt == Dataset.Ctrl)) %>%
    left_join(data.caus %>% select(Dataset.Trt, Dataset.Ctrl) %>% 
                mutate(Dataset.Trt=as.character(Dataset.Trt), Dataset.Ctrl=as.character(Dataset.Ctrl),
                       exists=TRUE),
              by=c("Dataset.Trt"="Dataset.Trt", "Dataset.Ctrl"="Dataset.Ctrl")) %>%
    filter(is.na(exists)) %>%
    mutate(Dataset.Trt=factor(Dataset.Trt, levels=dset.ord.site$Dataset,
                              ordered=TRUE),
           Dataset.Ctrl=factor(Dataset.Ctrl, levels=dset.ord.site$Dataset,
                               ordered=TRUE))
  
  
  data.caus %>%
    ggplot(aes(x=Dataset.Trt, y=Dataset.Ctrl, alpha=p.value)) +
    geom_text(data=empty.df %>% arrange(Dataset.Ctrl, Dataset.Trt), label="\u2717", color='red',
              family="Arial Unicode MS", alpha=1) +
    geom_tile(aes(fill=Data)) +
    xlab("Dataset") +
    ylab("Dataset") +
    scale_alpha_continuous(trans=reverselog_trans(10), limits=c(1, .0004), breaks=c(.001, .01, .1, 1), 
                           labels=c(".001", ".01", ".1", "1"), name="p-value") +
    scale_fill_manual(values=c("Adjusted"="cornflowerblue", "Causal Cross."="purple", "Conditional"="orange","Associational"="red"), 
                      name="Estimated Effect") +
    # geom_point(data=sig.dat, aes(x=Dataset.Trt, y=Dataset.Ctrl), shape="\u2713", color='black') +
    geom_text(data=sig.dat, label="\u2713", color='black',
              family="Arial Unicode MS", alpha=1) +
    ggtitle(title) +
    theme_bw() +
    theme(text=element_text(size=text.size), axis.text.x=element_text(angle=90, hjust = 0.95, vjust=.2),
          panel.grid.major=element_blank(),
          panel.grid.minor = element_blank(),
          legend.position="bottom", legend.direction="horizontal", legend.box="vertical")
}

pval_hmap_chart.noncaus <- function(data, dset.ord.site, title="", alpha=.05, method="Raw", text.size=15, preproc=TRUE) {
  if (!preproc) {
    data <- data %>%
      filter(Method == method) %>%
      left_join((.) %>% filter(grepl("Causal", Data)) %>% 
                  select(Dataset.Ctrl, Dataset.Trt, Method) %>% mutate(has.causal=TRUE),
                by=c("Dataset.Ctrl", "Dataset.Trt", "Method")) %>%
      mutate(has.causal=ifelse(is.na(has.causal), FALSE, TRUE))
  }
  
  dset.ord.trt <- dset.ord.site %>%
     rename(n.trt=n, Dataset.Trt= Dataset, id.trt=id) %>%
     select(n.trt, Dataset.Trt, id.trt)
  dset.ord.ctrl <- dset.ord.site %>%
     rename(n.ctrl=n, Dataset.Ctrl= Dataset, id.ctrl=id) %>%
     select(n.ctrl, Dataset.Ctrl, id.ctrl)
  # data <- data %>% filter(Data %in% c("Adjusted", "Causal Cross.", "Associational")) %>%
  #   filter(!(Data == "Adjusted" & grepl("NKI", Dataset.Trt) & grepl("NKI", Dataset.Ctrl)))
  data.ncaus <- data %>%
    filter(Data %in% c("Associational", "Conditional")) %>%
    left_join(dset.ord.trt) %>%
    left_join(dset.ord.ctrl) %>%
    ungroup() %>%
    mutate(id.row=row_number()) %>%
    group_by(id.row) %>%
    mutate(Dataset.Trt.X=c(Dataset.Trt, Dataset.Ctrl)[which.min(c(id.trt, id.ctrl))],
           Dataset.Ctrl.X=c(Dataset.Trt, Dataset.Ctrl)[which.max(c(id.trt, id.ctrl))],
           Dataset.Trt=Dataset.Trt.X, Dataset.Ctrl=Dataset.Ctrl.X,
           Dataset.tmp=as.character(Dataset.Trt),
           Dataset.Trt=ifelse(grepl("Conditional", Data), as.character(Dataset.Ctrl), as.character(Dataset.Trt)),
           Dataset.Ctrl=ifelse(grepl("Conditional", Data), as.character(Dataset.tmp), as.character(Dataset.Ctrl)),
           Dataset.Trt=factor(Dataset.Trt,
                              levels=dset.ord.site$Dataset,
                              ordered=TRUE),
           Dataset.Ctrl=factor(Dataset.Ctrl,
                               levels=dset.ord.site$Dataset,
                               ordered=TRUE))
  
  sig.dat <- data.ncaus %>% filter(p.value < alpha)
  
  empty.df <- expand.grid(dset.ord.trt$Dataset.Trt, dset.ord.trt$Dataset.Trt) %>%
    rename(Dataset.Trt=Var1, Dataset.Ctrl=Var2) %>%
    filter(!(Dataset.Trt == Dataset.Ctrl)) %>%
    left_join(data.ncaus %>% select(Dataset.Trt, Dataset.Ctrl) %>% 
                mutate(Dataset.Trt=as.character(Dataset.Trt), Dataset.Ctrl=as.character(Dataset.Ctrl),
                       exists=TRUE),
              by=c("Dataset.Trt"="Dataset.Trt", "Dataset.Ctrl"="Dataset.Ctrl")) %>%
    filter(is.na(exists)) %>%
    mutate(Dataset.Trt=factor(Dataset.Trt, levels=dset.ord.site$Dataset,
                              ordered=TRUE),
           Dataset.Ctrl=factor(Dataset.Ctrl, levels=dset.ord.site$Dataset,
                               ordered=TRUE))
  
  
  data.ncaus %>%
    ggplot(aes(x=Dataset.Trt, y=Dataset.Ctrl, alpha=p.value)) +
    geom_tile(aes(fill=Data)) +
    xlab("Dataset") +
    ylab("Dataset") +
    scale_alpha_continuous(trans=reverselog_trans(10), limits=c(1, .0004), breaks=c(.001, .01, .1, 1), 
                           labels=c(".001", ".01", ".1", "1"), name="p-value") +
    scale_fill_manual(values=c("Adjusted"="cornflowerblue", "Causal Cross."="purple", "Conditional"="orange","Associational"="red"), 
                      name="Estimated Effect") +
    # geom_point(data=sig.dat, aes(x=Dataset.Trt, y=Dataset.Ctrl), shape="\u2713", color='black') +
    geom_text(data=sig.dat, label="\u2713", color='black',
              family="Arial Unicode MS", alpha=1) +
    ggtitle(title) +
    theme_bw() +
    theme(text=element_text(size=text.size), axis.text.x=element_text(angle=90, hjust = 0.95, vjust=.2),
          panel.grid.major=element_blank(),
          panel.grid.minor = element_blank(),
          legend.position="bottom", legend.direction="horizontal", legend.box="vertical")
}

pval_hist_chart <- function(data, nbreaks=30, title="", text.y=.8, method="Raw",
                            text.size=15, preproc=TRUE, p.adjust=.00005) {
  if (!preproc) {
    data <- data %>%
      mutate(Data=recode_factor(Data, "Untrimmed"="Associational", "Trimmed"="Propensity-Trimmed")) %>%
      filter(Method == method) %>%
      left_join((.) %>% filter(Data == "Propensity-Trimmed") %>% 
                  select(Dataset.Ctrl, Dataset.Trt, Method) %>% mutate(is.good=TRUE),
                by=c("Dataset.Ctrl", "Dataset.Trt", "Method")) %>%
      mutate(is.good=ifelse(is.na(is.good), FALSE, TRUE))
  }
  pval.breaks <- seq(0, 1, length.out=nbreaks)
  
  sum.n <- data %>%
    group_by(Data, Method) %>%
    summarize(count=n()) %>%
    mutate(text=sprintf("n=%d", count), size=1/count) %>%
    ungroup()
  
  data.rand <- data %>% sample_n(nrow(.)) %>%
    left_join(sum.n %>% select(Data, size))
  plt <- data %>%
    arrange(Data) %>%
    ggplot() +
      geom_histogram(aes(p.value, color=Data, fill=Data,
                         group=paste0(Data, Method),
                         y=..count../tapply(..count.., ..group.., sum)[..group..]),
                     alpha=.5, position="dodge") +
      geom_jitter(data=data.rand, aes(p.value, size=size, group=paste0(Data), y=-3/2*.1, fill=Data,
                      color=Data), width=1000*ggplot2:::resolution(log10(results$Site$p.value), FALSE),
                  height=.1) +
      facet_grid("Data~.") +
      geom_text(data=data.frame(x=.1, y=text.y/2, Data="Associational", text="$\\alpha$=.05"),
              aes(x=x, y=y, label=TeX(text, output="character")), 
              nudge_x=.2, color='black', parse=TRUE) +
      geom_text(data=sum.n, aes(x=.45, y=text.y, label=text, color=Data), nudge_x=-.15) +
      scale_fill_manual(values=c("Associational"="orange", "Conditional"="blue", "Adjusted"="cornflowerblue", "Causal Cross."="purple"), name="Estimated Effect") +
      scale_color_manual(values=c("Associational"="orange", "Conditional"="blue", "Adjusted"="cornflowerblue", "Causal Cross."="purple")) +
      scale_x_continuous(expand=c(0, 0), limits=c(.0004, 1), breaks=c(.001, .01, .1, 1),
                         label=c(".001", ".01", ".1", "1"), trans="log10") +
      scale_y_continuous(expand=c(0, 0.03), limits=c(-.25, 1), breaks=c(0, .5, 1)) +
      scale_size(range=c(0, 1)) +
      xlab("p-value") +
      ylab("Proportion") +
      ggtitle(title) +
      theme_bw() +
      theme(text=element_text(size=text.size)) +
      geom_vline(xintercept = .05, linetype="dashed") +
      guides(fill=FALSE, shape=FALSE, color=FALSE, size=FALSE)
  return(as.ggplot(gtable_filter(ggplotGrob(plt), "axis-b-[2,3]", trim=FALSE, invert=TRUE)))
}

compare_site <- function(data, dset.ord.site, method="Raw", nbreaks=30, text.y=.8, y.scale=.03, title.hmap="",
                         title.hist="", text.size=15, p.adjust=0) {
  data <- data %>%
    filter(Method == method) %>%
    left_join((.) %>% filter(grepl("Causal", Data)) %>% 
                select(Dataset.Ctrl, Dataset.Trt, Method) %>% mutate(has.causal=TRUE),
              by=c("Dataset.Ctrl", "Dataset.Trt", "Method")) %>%
    mutate(has.causal=ifelse(is.na(has.causal), FALSE, TRUE))
  
  p.hmap <- pval_hmap_chart(data, dset.ord.site, method=method, title=title.hmap, text.size=text.size)
  p.hist <- pval_hist_chart(data, method=method, nbreaks=nbreaks, title=title.hist,
                            text.y=text.y, text.size=text.size, p.adjust=p.adjust)
  arrangeGrob(p.hmap, p.hist, widths=c(.6, .6), nrow=1)
}
```

```{r, fig.height=7, fig.width=13}
#plot(compare_site(results$Site, dset.ord.site, title.hmap="(A) Estimated Effect per Pair of Datasets",
#             title.hist="(B) Empirical Distribution of Estimated Effects"))
plt.caus <- pval_hmap_chart(results$Site, dset.ord.site, preproc=FALSE, title="(B) Demographic-Adjusted Effects")
plt.noncaus <- pval_hmap_chart.noncaus(results$Site, dset.ord.site, preproc=FALSE, title="(A) Effects without Demographic Adjustment")

plt.comb <- arrangeGrob(plt.noncaus, plt.caus, ncol=2)
ggsave('../Folder/raw_pairwise.svg', plot=plt.comb, width=13, height=7)
```

```{r}
pval_hist_chart(results$Site, preproc=FALSE,title="Empirical Distribution of Estimated Effects")
```

```{r, fig.height=8, fig.width=9.5}
results$Site <- results$Site %>%
  filter(Method != "Ranked") %>%
  mutate(Method=factor(Method, levels=c("Raw", "Z-Score", "ComBat", "causal ComBat"), ordered=TRUE))

graph2df_site <- function(gr, dset=NULL, method=NULL) {
  graph2df(gr) %>%
    mutate(Dataset=dset, Method=method)
}

get_site_gr <- function(data, site1="BNU1", site2="SWU4") {
  do.call(rbind, lapply(names(data), function(norm) {
    x <- data[[norm]]
    g1 = x$Dataset[[site1]]$All
    g2 = x$Dataset[[site2]]$All
    gdiff = abs(g1 - g2)
    rbind(graph2df_site(g1, site1, norm), graph2df_site(g2, site2, norm), 
          graph2df_site(gdiff, sprintf("|%s - %s|", site1, site2), norm))
  }))
}

site1="MRN1"; site2="IBATRT"
con.plt <- get_site_gr(results$Stats, site1, site2) %>%
  filter(!(Method %in% c("Ranked", "conditional ComBat"))) %>%
  mutate(Dataset=factor(Dataset, levels=c(site1, site2, 
                                          sprintf("|%s - %s|", site1, site2)),
                        ordered=TRUE),
         Method=factor(Method, levels=c("Raw", "Z-Score", "ComBat", "causal ComBat"), ordered=TRUE)) %>%
  ggplot(aes(x=reorder(Row, Row.mod2), y=reorder(Column, Col.mod2), fill=Value)) +
  geom_tile() +
  scale_x_discrete(breaks=c(), name="Parcel") +
  scale_y_discrete(breaks=c(), name="Parcel") +
  facet_grid(Dataset ~ Method) +
  scale_fill_gradient(high="#530481", low="#fdf2fe", name="Weight", breaks=c(0, .5, 1),
                      limits=c(-.000001, 1)) +
  theme_bw() +
  theme(text=element_text(size=15)) +
  ggtitle("(A) Average Connectomes Across 2 Datasets with Similar Covariate Distribution")

con.leg <- get_legend(con.plt); con.plt <- con.plt + guides(fill=FALSE)
con.plt <- as.ggplot(gtable_filter(ggplotGrob(con.plt), "axis-b-[2,3,4]|axis-l-[2,3]", trim=FALSE, invert=TRUE))

diff.conns <- graph2df(abs(results$Stats$Raw$Dataset$NYU2$Male -
  results$Stats$Raw$Dataset$NYU2$Female)) %>%
  mutate(Method="Raw", Title="|NYU2, M - NYU2, Fm|") %>%
  rbind(
    graph2df(abs(results$Stats$Raw$Dataset$NYU2$Male -
  results$Stats$Raw$Dataset$Utah1$All)) %>%
    mutate(Method="Raw", Title="|NYU2, M - Utah1|"),
    graph2df(abs(results$Stats$ComBat$Dataset$NYU2$Male -
  results$Stats$ComBat$Dataset$NYU2$Female)) %>%
    mutate(Method="ComBat", Title="|NYU2, M - NYU2, Fm|"),
    graph2df(abs(results$Stats$ComBat$Dataset$NYU2$Male -
  results$Stats$ComBat$Dataset$Utah1$All)) %>%
    mutate(Method="ComBat", Title="|NYU2, M - Utah1|")
  ) %>%
  mutate(Title=factor(Title, levels=c("|NYU2, M - NYU2, Fm|",
                                      "|NYU2, M - Utah1|"), ordered=TRUE),
         Method=factor(Method, levels=c("Raw", "ComBat"), ordered=TRUE))

combt.issues <- diff.conns %>%
  # normalize
  mutate(Value = (Value - min(Value))/(max(Value) - min(Value))) %>%
  ggplot(aes(x=reorder(Row, Row.mod2), y=reorder(Column, Col.mod2), fill=Value)) +
  geom_tile() +
  scale_x_discrete(breaks=c(), name="Parcel") +
  scale_y_discrete(breaks=c(), name="Parcel") +
  facet_nested(.~Title +Method) +
  scale_fill_gradient(high="#530481", low="#fdf2fe", name="Weight", breaks=c(0, .5, 1),
                      limits=c(-.000001, 1)) +
  theme_bw() +
  theme(text=element_text(size=15)) +
  ggtitle("(B) ComBat Removes Biological Variability")

diff.adj <- graph2df(abs(results$Stats$`Raw`$Dataset$NYU2$All -
  results$Stats$`Raw`$Dataset$IBATRT$All)) %>%
  mutate(Title="Raw") %>%
  rbind(
    graph2df(abs(results$Stats$`ComBat`$Dataset$NYU2$All -
  results$Stats$`ComBat`$Dataset$IBATRT$All)) %>%
    mutate(Title="ComBat"),
    graph2df(abs(results$Stats$`causal ComBat`$Dataset$NYU2$All -
  results$Stats$`causal ComBat`$Dataset$IBATRT$All)) %>%
    mutate(Title="causal ComBat")
  ) %>%
  mutate(Title=factor(Title, levels=c("Raw", "ComBat", "causal ComBat"), ordered=TRUE))

adj.issues <- diff.adj %>%
  # normalize
  mutate(Value = (Value - min(Value))/(max(Value) - min(Value))) %>%
  ggplot(aes(x=reorder(Row, Row.mod2), y=reorder(Column, Col.mod2), fill=Value)) +
  geom_tile() +
  scale_x_discrete(breaks=c(), name="Parcel") +
  scale_y_discrete(breaks=c(), name="Parcel") +
  facet_grid(.~Title) +
  scale_fill_gradient(high="#530481", low="#fdf2fe", name="Weight", breaks=c(0, .5, 1),
                      limits=c(-.000001, 1)) +
  theme_bw() +
  theme(text=element_text(size=15)) +
  ggtitle("(C) Causal ComBat does not Remove Adjusted Effects")


plt <- arrangeGrob(con.plt, combt.issues, adj.issues, heights=c(.9, .37, .4))
grid.arrange(plt)

plot(con.plt)
```

```{r}

results.utah1 <- results$Site %>%
  filter((Dataset.Trt == "Utah1" | Dataset.Ctrl == "Utah1")) %>%
  filter(Method == "ComBat") %>%
  filter(Data == "Associational")

hist.comBat <- results.utah1 %>%
  ggplot() +
  geom_histogram(aes(p.value, 
                         group=paste0(Data, Method),
                         y=..count../tapply(..count.., ..group.., sum)[..group..]),
                     alpha=.5, position="identity", color='red', fill='red') +
      geom_jitter(data=results.utah1 %>% slice(sample(1:n())), aes(p.value, group=paste0(Data), y=-3/2*.1),
                  color='red', fill='red',width=1000*ggplot2:::resolution(log10(results$Site$p.value), FALSE),
                  height=.1, size=.02) +
      facet_grid(.~Method) +
      geom_text(data=data.frame(x=.05, y=.5, Method=as.factor("ComBat"), text="$\\alpha$=.05"),
              aes(x=x, y=y, label=TeX(text, output="character")), 
              nudge_x=.5, color='black', parse=TRUE) +
      # scale_fill_manual(values=c("Associational"="red", "Conditional"="blue", "Adjusted"="cornflowerblue", "Causal Cross."="purple"), name="Estimated Effect") +
      # scale_color_manual(values=c("Associational"="red", "Conditional"="blue", "Adjusted"="cornflowerblue", "Causal Exp."="purple"), name="Estimated Effect") +
      scale_x_continuous(expand=c(0, 0), limits=c(.0002, 1.2), labels=c(".001", ".01", ".1", "1"),
                         breaks=c(.001, .01, .1, 1), trans="log10") +
      scale_y_continuous(expand=c(0, 0.03), limits=c(-.25, 1), breaks=c(0, .5, 1)) +
      xlab("p-value") +
      ylab("Proportion") +
      ggtitle("(A) ComBat Removes Biological Variability from Utah 1") +
      theme_bw() +
      theme(text=element_text(size=15), strip.background.y = element_rect(fill="white", color="white")) +
      geom_vline(xintercept = .05, linetype="dashed") +
      guides(shape=FALSE)


results.cc <- results$Site %>%
  filter(Method == "causal ComBat") %>%
  filter(Data == "Adjusted")

hist.cc <- results.cc %>%
  ggplot() +
  geom_histogram(aes(p.value, 
                         group=paste0(Data, Method),
                         y=..count../tapply(..count.., ..group.., sum)[..group..]),
                     alpha=.5, position="identity", color='cornflowerblue', fill='cornflowerblue') +
      geom_jitter(data=results.cc %>% slice(sample(1:n())), aes(p.value, group=paste0(Data), y=-3/2*.1),
                  color='cornflowerblue', fill='cornflowerblue',width=1000*ggplot2:::resolution(log10(results$Site$p.value), FALSE),
                  height=.1, size=.02) +
      facet_grid(.~Method) +
      geom_text(data=data.frame(x=.05, y=.5, Method=as.factor("causal ComBat"), text="$\\alpha$=.05"),
              aes(x=x, y=y, label=TeX(text, output="character")), 
              nudge_x=.5, color='black', parse=TRUE) +
      # scale_fill_manual(values=c("Associational"="red", "Conditional"="blue", "Adjusted"="cornflowerblue", "Causal Cross."="purple"), name="Estimated Effect") +
      # scale_color_manual(values=c("Associational"="red", "Conditional"="blue", "Adjusted"="cornflowerblue", "Causal Exp."="purple"), name="Estimated Effect") +
      scale_x_continuous(expand=c(0, 0), limits=c(.0002, 1.2), labels=c(".001", ".01", ".1", "1"),
                         breaks=c(.001, .01, .1, 1), trans="log10") +
      scale_y_continuous(expand=c(0, 0.03), limits=c(-.25, 1), breaks=c(0, .5, 1)) +
      xlab("p-value") +
      ylab("Proportion") +
      ggtitle("(B) causal ComBat does not Remove Adjusted Effects") +
      theme_bw() +
      theme(text=element_text(size=15), strip.background.y = element_rect(fill="white", color="white")) +
      geom_vline(xintercept = .05, linetype="dashed") +
      guides(shape=FALSE)


plt <- arrangeGrob(con.plt, arrangeGrob(hist.comBat, hist.cc, nrow=1), heights=c(.9, .4))
grid.arrange(plt)
```

```{r, fig.height=6.5, fig.width=10}
hist.plt.all <- results$Site %>%
  ggplot() +
  geom_histogram(aes(p.value, 
                         group=paste0(Data, Method), fill=Data, color=Data,
                         y=..count../tapply(..count.., ..group.., sum)[..group..]),
                     alpha=.5, position="identity") +
      geom_jitter(data=results$Site %>% slice(sample(1:n())), aes(p.value, group=paste0(Data), y=-3/2*.1,
                                                                  color=Data, fill=Data),
                  width=1000*ggplot2:::resolution(log10(results$Site$p.value), FALSE),
                  height=.1, size=.02) +
      facet_grid(Data~Method) +
      geom_text(data=data.frame(x=.05, y=.5, Method=as.factor("Raw"), Data=as.factor("Associational"), text="$\\alpha$=.05"),
              aes(x=x, y=y, label=TeX(text, output="character")), 
              nudge_x=.6, color='black', parse=TRUE) +
      scale_fill_manual(values=c("Associational"="red", "Conditional"="blue", "Adjusted"="cornflowerblue", "Causal Cross."="purple"), name="Estimated Effect") +
      scale_color_manual(values=c("Associational"="red", "Conditional"="blue", "Adjusted"="cornflowerblue", "Causal Cross."="purple"), name="Estimated Effect") +
      scale_x_continuous(expand=c(0, 0), limits=c(.0002, 1.2), labels=c(".001", ".01", ".1", "1"),
                         breaks=c(.001, .01, .1, 1), trans="log10") +
      scale_y_continuous(expand=c(0, 0.03), limits=c(-.25, 1), breaks=c(0, .5, 1)) +
      xlab("p-value") +
      ylab("Proportion") +
      ggtitle("Detection of Batch and Measurement Effects by Correction Strategy") +
      theme_bw() +
      theme(text=element_text(size=15)) +
      geom_vline(xintercept = .05, linetype="dashed") +
      guides(shape=FALSE)

as.ggplot(gtable_filter(ggplotGrob(hist.plt.all), 
                        "axis-b-[2,3,4]", trim=FALSE, invert=TRUE))
```

### Between-Individual Covariate Effects

```{r}
results$Covariate <- results$Covariate %>%
  ungroup() %>%
  mutate(p.value=p.adjust(p.value, method="BH")) %>%
  filter(Variance > 0)
```

```{r, fig.height=10, fig.width=13}
results.cov <- results$Covariate %>%
  filter(Method != "Ranked") %>%
  mutate(Method=factor(Method, levels=c("Raw", "causal ComBat", "ComBat", "Z-Score"), ordered=TRUE))


cov.combt <- results.cov %>% filter(Method == "causal ComBat")
results.cov <- rbind(cov.combt, results.cov %>% 
                             filter(Method != "Ranked"))
results.cov <- results.cov %>%
  filter(Method != "Raw") %>%
  left_join(results.cov %>% filter(Method == "Raw") %>% 
              select(p.value, Dataset, Effect.Name) %>% rename(p.value.raw=p.value),
            by=c("Dataset", "Effect.Name"))
```

```{r, fig.height=9.5, fig.width=11}
graph2df <- function(gr, covar=NULL, lev=NULL, method=NULL) {
  rownames(gr) <- 1:dim(gr)[1]
  colnames(gr) <- 1:dim(gr)[2]
  data.frame(gr) %>%
    mutate(Row=row_number()) %>%
    pivot_longer("X1":sprintf("X%d", dim(gr)[2]), names_to="Column", values_to="Value") %>%
    mutate(Column=gsub("X", "", Column), Column=factor(Column, levels=colnames(gr), ordered=TRUE),
           Row=factor(Row, levels=rownames(gr), ordered=TRUE),
           Covariate=covar, Level=lev, Method=method)
}

get_site_gr <- function(data, site="NYU2") {
  name.dat <- names(data)
  name.dat <- name.dat[name.dat != "Ranked"]
  do.call(rbind, lapply(name.dat, function(norm) {
    x <- data[[norm]]
    male.g = x$Dataset[[site]]$Male
    female.g = x$Dataset[[site]]$Female
    gdiff.gender = abs(male.g - female.g)
    
    young.g = x$Dataset[[site]]$Young
    old.g = x$Dataset[[site]]$Old
    gdiff.age = abs(young.g - old.g)
    rbind(#graph2df(male.g, "Sex", "Male", norm), graph2df(female.g, "Sex", "Female", norm),
          graph2df(gdiff.gender, "Sex", "|Male - Female|", norm),
          #graph2df(young.g, "Age", "Young", norm), graph2df(old.g, "Age", "Old", norm),
          graph2df(gdiff.age, "Age", "|Young - Old|", norm)) %>%
      mutate(Method=factor(Method, levels=c("Raw", "causal ComBat", "ComBat", "Z-Score"), ordered=TRUE),
             Covariate=factor(Covariate, levels=c("Sex", "Age"), ordered=TRUE),
             # Level=factor(Level, levels=c("Male", "Female", "|Male - Female|", "Young", "Old", "|Young - Old|")))
             Level=factor(Level, levels=c( "|Male - Female|", "|Young - Old|")))
  }))
}

site="NYU2"
con.plt <- get_site_gr(results$Stats, site) %>%
  mutate(Row.mod2=as.numeric(Row) %% 2, Col.mod2 = as.numeric(Column) %% 2) %>%
  group_by(Level, Covariate, Method) %>%
  mutate(Value=(Value - min(Value))/(max(Value) - min(Value))) %>%
  ggplot(aes(x=reorder(Row, Row.mod2), y=reorder(Column, Col.mod2), fill=Value)) +
  geom_tile() +
  scale_x_discrete(breaks=c(), name="Parcel") +
  scale_y_discrete(breaks=c(), name="Parcel") +
  facet_nested(Covariate + Level~Method) +
  scale_fill_gradient(high="#530481", low="#fdf2fe", name="Normalized Weight") +
  theme_bw() +
  theme(text=element_text(size=15)) +
  ggtitle("(A) Conditional Average Connectomes Across NYU2")

con.leg <- get_legend(con.plt); con.plt <- con.plt + guides(fill=FALSE)
con.plt <- as.ggplot(gtable_filter(ggplotGrob(con.plt), "axis-b-[2,3,4,5,6]|axis-l-[2,3,4]", trim=FALSE, invert=TRUE))

scatter.cov <- results.cov %>% slice(sample(1:n())) %>%
  mutate(Cohort=ifelse(Dataset %in% c("NYU2", "IBATRT", "MRN1", "UWM", "NYU1"),
                       "American", "Other")) %>%
  filter(Cohort == "American") %>%
  ggplot() +
  geom_point(aes(x=p.value.raw, y=p.value, color=Effect.Name, shape=Effect.Name), size=2) +
  facet_grid(".~Method") +
  scale_color_manual(values=c("Sex"="springgreen4", "Age"="orange"), name="Covariate") +
  scale_shape(name="Covariate") +
  theme_bw() +
  xlab("p-value Before Adjustment (log)") +
  ylab("p-value After Adjustment (log)") +
  scale_x_continuous(expand=c(0, 0), limits=c(.0004, 1), breaks=c(.001, .01, .1, 1),
                     labels=c(".001", ".01", ".1", "1"), trans="log10") +
  scale_y_continuous(expand=c(0, 0), limits=c(.0004, 1), breaks=c(.001, .01, .1, 1),
                     labels=c(".001", ".01", ".1", "1"), trans="log10") +
  ggtitle("(B) Impact of Site Correction on Covariate Effects") +
  theme(text=element_text(size=15)) +
  geom_vline(data=data.frame(Method=c("causal ComBat", "ComBat", "Z-Score")), aes(xintercept=.05), linetype="dashed") +
  geom_hline(data=data.frame(Method=c("causal ComBat", "ComBat", "Z-Score")), aes(yintercept=.05), linetype="dashed") + 
  geom_text(data=data.frame(Method=c("causal ComBat")),
              aes(x=.25, y=.03, label=TeX("$\\alpha$=.05", output="character")), 
              color='black', parse=TRUE) +
  geom_abline(intercept=0, slope=1, size=1.001, color="#530481") +
  geom_text(data=data.frame(Method=c("causal ComBat")),
            aes(x=.005, y=.002, label=TeX("$y=x$", output="character")), color="#530481", parse=TRUE)
cov.leg <- get_legend(scatter.cov); scatter.cov <- scatter.cov + guides(shape=FALSE, color=FALSE)

scatter.cov <- as.ggplot(gtable_filter(ggplotGrob(scatter.cov), "axis-b-[2,3]", trim=FALSE, invert=TRUE))

plt <- arrangeGrob(arrangeGrob(con.plt, scatter.cov, heights=c(.7, .5)), 
                   arrangeGrob(con.leg, cov.leg, heights=c(.7, .5)),
                   widths=c(.9, .2))

grid.arrange(plt)
```


### Looking at Signal Preservation

```{r, fig.width=9.7, fig.height=7.5, message=FALSE}
graph2df <- function(gr, name=NULL, method=NULL) {
  rownames(gr) <- 1:dim(gr)[1]
  colnames(gr) <- 1:dim(gr)[2]
  data.frame(gr) %>%
    mutate(Row=row_number()) %>%
    pivot_longer("X1":sprintf("X%d", dim(gr)[2]), names_to="Column", values_to="Value") %>%
    mutate(Column=gsub("X", "", Column), Column=factor(Column, levels=colnames(gr), ordered=TRUE),
           Row=factor(Row, levels=rownames(gr), ordered=TRUE),
           Name=name, Method=method)
}

results$Signal <- results$Signal %>%
  mutate(p.value=p.adjust(p.value, method="BH"))

get_sig_gr <- function(data, site="NYU2") {
  do.call(rbind, lapply(names(data), function(norm) {
    x <- data[[norm]]
    g = x$Dataset[[site]]$Male.Young
    
    graph2df(g, method=norm, name="Homophilic") %>% mutate(Color=NA)
  })) %>%
    rbind(graph2df(matrix(parcel.comm$AAL$Homophilic, nrow=116), method="Community", name="Homophilic") %>%
            filter(!is.nan(Value)) %>%
            mutate(Color=ifelse(Value == 1, "Homophilic", "non-Homophilic"), Value=NA),
          graph2df(matrix(parcel.comm$AAL$Homotopic, nrow=116), method="Community", name="Homotopic") %>%
            filter(!is.nan(Value)) %>%
            mutate(Color=ifelse(Value == 1, "Homotopic", "non-Homotopic"),  Value=NA))
}

con.dat <- get_sig_gr(results$Stats) %>%
  filter(Method != "Ranked") %>%
  mutate(Row.mod2=as.numeric(Row) %% 2, Col.mod2 = as.numeric(Column) %% 2,
         Method=factor(Method, levels=c("Community", "Raw", "causal ComBat", "ComBat", "Z-Score"), ordered=TRUE)) %>%
  group_by(Name, Method) %>%
  mutate(Value=(Value - min(Value))/(max(Value) - min(Value)))

con.plt <- arrangeGrob(
  ggplot(con.dat %>% filter(Method == "Community") %>%
           mutate(Color=factor(Color, levels=c("Homophilic", "non-Homophilic",
                                    "Homotopic", "non-Homotopic"), ordered=TRUE)), aes(x=reorder(Row, Row.mod2),
                       y=reorder(Column, Col.mod2), fill=Color)) +
    geom_tile() +
    facet_grid(.~ Name) +
    scale_x_discrete(breaks=c(), name="") +
    scale_y_discrete(breaks=c(), name="Parcel") +
    scale_fill_manual(values=c("Homophilic"="red", "non-Homophilic"="rosybrown3", "Homotopic"="blue",
                               "non-Homotopic"="skyblue"), name="Edge Community") +
    theme_bw() +
    theme(strip.background = element_rect(color = "white", fill="white"),
          strip.text=element_text(color="white"),
          text=element_text(size=15)),
  ggplot(con.dat %>% filter(Method != "Community"), aes(x=reorder(Row, Row.mod2),
                     y=reorder(Column, Col.mod2), fill=Value)) +
    geom_tile() +
    facet_grid(. ~ Method) +
    scale_x_discrete(breaks=c(), name="Parcel") +
    scale_y_discrete(breaks=c(), name="") +
    scale_fill_gradient(high="#530481", low="#fdf2fe", name="Normalized Weight") +
    theme_bw() + theme(text=element_text(size=15)),
  widths=c(.4, .7), top=textGrob("(A) Normalized Connectome, Before and After Correction, for a Single Individual", gp=gpar(fontsize=18),
                                 hjust = .66))

get_comm_wts <- function(data, site="NYU2") {
  do.call(rbind, lapply(names(data), function(norm) {
    x <- data[[norm]]
    g = x$Dataset[[site]]$Male.Young
    
    homo.edge = parcel.comm$AAL$Homotopic  == 1 & !is.na(parcel.comm$AAL$Homotopic  == 1)
    nohomo.edge = parcel.comm$AAL$Homotopic  == 0 & !is.na(parcel.comm$AAL$Homotopic  == 0)
    
    homop.edge = parcel.comm$AAL$Homophilic  == 1 & !is.na(parcel.comm$AAL$Homophilic  == 1)
    nohomop.edge = parcel.comm$AAL$Homophilic  == 0 & !is.na(parcel.comm$AAL$Homophilic  == 0)
    rbind(data.frame(Value=g[homop.edge & upper.tri(g)], Method=norm, Group="Homophilic",
                     Comm="Homophilic"),
          data.frame(Value=g[nohomop.edge & upper.tri(g)], Method=norm, Group="Homophilic",
                     Comm="non-Homophilic"),
          data.frame(Value=g[homo.edge & upper.tri(g)], Method=norm, Group="Homotopic",
                     Comm="Homotopic"),
          data.frame(Value=g[nohomo.edge & upper.tri(g)], Method=norm, Group="Homotopic",
                     Comm="non-Homotopic"))
  }))
}

edge.dat <- get_comm_wts(results$Stats) %>%
  filter(Method != "Ranked") %>%
  group_by(Method) %>%
  mutate(Value=(Value - min(Value))/(max(Value) - min(Value)),
         Method=factor(Method, levels=c("Raw", "causal ComBat", "ComBat", "Z-Score"), ordered=TRUE),
         Comm=factor(Comm, levels=c("Homophilic", "non-Homophilic",
                                    "Homotopic", "non-Homotopic"), ordered=TRUE))

edge.dat <- rbind(edge.dat %>% filter(Group == "Homophilic") %>% slice(sample(1:n())),
                  edge.dat %>% filter(Group == "Homotopic") %>% arrange(desc(Comm))) %>%
  filter(Method != "Ranked")

hist.plt <- edge.dat %>% ungroup() %>%
  ggplot() +
  geom_histogram(aes(Value, color=Comm, fill=Comm, group=paste0(Group, Comm, Method),
                     y=..count../tapply(..count.., ..group.., sum)[..group..]),
                     alpha=.5, position="identity") +
  geom_jitter(data=edge.dat %>%
  group_by(Method, Comm) %>%
  mutate(ID=row_number()) %>%
  filter(ID <= 1000),
              aes(Value, group=paste0(Group, Comm, Method),
                  y=-.02, fill=Comm, color=Comm),
              width=.01,
              height=.015, size=.01) +
  ylab("Proportion") +
  xlab("Normalized Weight") +
  ggtitle("Normalized Edge Weights, Before and After Correction, for a Single Individual") +
  facet_grid(Group ~ Method) +
    scale_fill_manual(values=c("Homophilic"="red", "non-Homophilic"="rosybrown3", "Homotopic"="blue",
                               "non-Homotopic"="skyblue"), name="Edge Community") +
    scale_color_manual(values=c("Homophilic"="red", "non-Homophilic"="rosybrown3", "Homotopic"="blue",
                               "non-Homotopic"="skyblue"), name="Edge Community") +
  theme_bw() +
  theme(text=element_text(size=15))
hist.plt <- as.ggplot(gtable_filter(ggplotGrob(hist.plt), "axis-b-[2,3,4]|axis-l-2", trim=FALSE, invert=TRUE))

dat.sig <- results$Signal %>%
  filter(Method == "causal ComBat") %>%
  select(Dataset, Subid, Session, Signal, Effect.Size, Effect.Size, Community) %>%
  rename("causal ComBat"=Effect.Size) %>%
  left_join(results$Signal %>% filter(Method != "causal ComBat") %>%
              group_by(Dataset, Subid, Session, Community, Parcellation, Modality) %>%
              select(-Signal, -p.value) %>%
              pivot_wider(names_from="Method", values_from="Effect.Size"),
            by=c("Dataset", "Subid", "Session", "Community")) %>%
  mutate(Community=recode_factor(Community, "Homophilic"="Homophilic Difference",
                                 "Homotopic"="Homotopic Difference")) %>%
  pivot_longer(c("causal ComBat", "ComBat", "Ranked", "Z-Score"), names_to="Method", values_to="Effect.Size") %>%
  filter(Method != "Ranked")
diag_line <- dat.sig %>%
  group_by(Community) %>%
  summarize(x.pt1=min(Raw), x.pt2=max(Raw),
         y.pt1=min(Effect.Size), y.pt2=max(Effect.Size)) %>%
  pivot_longer(names_to=c(".value", "Point"), names_pattern="(.*)\\.(.*)",
               cols=-Community) %>%
  group_by(Community, Point) %>%
  mutate(val=ifelse(Point == "pt1", min(x, y), max(x,y)))

plt <- dat.sig %>%
  slice(sample(1:n())) %>%
  ggplot(aes(x=Raw, y=Effect.Size)) +
    geom_point(aes(color=Method, shape=Method)) +
    geom_line(data=diag_line, aes(x=val, y=val), color="black", size=1.25) +
    geom_text(data=data.frame(x=5400000, y=5500000, Community="Homophilic Difference", text="$y=x"),
            aes(x=x, y=y, label=TeX(text, output="character")), 
            nudge_x=.2, color='black', parse=TRUE) +
    facet_wrap(Community~., scale="free") +
    xlab("Effect Size (Raw)") +
    ylab("Effect Size (Corrected)") +
    ggtitle("(B) Within-Individual Signal by Correction Method") +
    scale_color_manual(values = c("Raw"="chartreuse4", "causal ComBat"="#377eb8", "Z-Score"="#4daf4a", "ComBat"="red")) +
    theme_bw() +
    theme(text=element_text(size=15))

grid.arrange(con.plt, plt, heights=c(.35, .4))
```

```{r}

```


```{r}
plt <- results$Signal %>%
  filter(Community != "Upper.Tri" & Method != "Ranked") %>%
  filter(Dataset %in%  c("NYU2", "IBATRT", "MRN1", "UWM", "NYU1")) %>%
  mutate(Measure=recode_factor(Community, "Homophilic"="Homophilic Difference", "Homotopic"="Homotopic Difference"),
         Method=factor(Method, ordered=TRUE, levels=c("Raw", "causal ComBat", "ComBat", "Z-Score")),
         p.value=p.adjust(p.value, method="BH")) %>%
  ggplot(aes(p.value, color=Method)) +
  stat_ecdf(aes(linetype=Method), geom="step", size=1.02) +
    facet_grid(". ~ Measure") +
    scale_color_manual(values = c("Raw"="chartreuse4", "causal ComBat"="blue", "Z-Score"="red", "ComBat"="darkred")) +
    scale_linetype_manual(values = c("Raw"="solid", "causal ComBat"="dashed", "Z-Score"="solid", "ComBat"="dotted")) +
    xlab("p-value") +
    scale_x_continuous(limits=c(0, 1), expand=c(0.005,0.005)) +
    scale_y_continuous(limits=c(0, 1), expand=c(0,0.01)) +
    ylab("Cumulative Distribution") +
    geom_vline(xintercept = .05, size=1.02, linetype='dashed') +
    theme_bw() +
    ggtitle("(B) Detectability of Within-Individual Signal by Adjustment Technique") +
    geom_text(data=data.frame(x=.05, y=.8,Measure="Homophilic Difference", text="$\\alpha$=.05"),
            aes(x=x, y=y, label=TeX(text, output="character")), 
            nudge_x=.1, color='black', size=5, parse=TRUE) +
  theme(text=element_text(size=15))
plt <- as.ggplot(gtable_filter(ggplotGrob(plt), "axis-b-2", trim=FALSE, invert=TRUE))

grid.arrange(con.plt, plt, heights=c(.35, .4))
```

```{r, fig.height=3.8, fig.width=10}
plot(hist.plt)
```

## By Correction Technique Distances

```{r}
preproc <- readRDS('../data/dcorr/inputs_fMRI_AAL.rds')
```

```{r}
Dmtxs <- do.call(rbind, lapply(unique(results$Site$Method), function(method) {
  results.meth <- results$Site %>% filter(Method == method)
  Dmtx.meth <- preproc[[method]]$D
  cov.meth <- preproc[[method]]$covariates
  overlaps <- results$Site %>%
    filter(Method == method) %>%
    select(Dataset.Trt, Dataset.Ctrl, Overlap) %>%
    rbind((.) %>% 
            mutate(Dataset.Tmp=Dataset.Trt, Dataset.Trt=Dataset.Ctrl, Dataset.Ctrl=Dataset.Tmp) %>%
            select(-Dataset.Tmp))
  
  cov.meth <- cov.meth %>% mutate(id=sprintf("Sub-%d_Ses-%d", Subid, Session))
  rownames(Dmtx.meth) <- colnames(Dmtx.meth) <- cov.meth$id
  Dmtx.meth[lower.tri(Dmtx.meth, diag=TRUE)] <- NA
  
  Dmtx.long <- melt(Dmtx.meth) %>%
    filter(!is.na(value)) %>%
    rename(id.x=Var1, id.y=Var2, Distance=value) %>%
    left_join(cov.meth %>% 
                select(Age, Dataset, Sex, Subid, id) %>% 
                rename(Dataset.x=Dataset, Age.x=Age, Subid.x=Subid, Sex.x=Sex),
              by=c("id.x"="id")) %>%
    left_join(cov.meth %>% 
                select(Age, Dataset, Sex, Subid, id) %>% 
                rename(Dataset.y=Dataset, Age.y=Age, Subid.y=Subid, Sex.y=Sex),
              by=c("id.y"="id")) %>%
    left_join(overlaps %>% mutate(Dataset.Trt=as.character(Dataset.Trt), Dataset.Ctrl=as.character(Dataset.Ctrl)),
              by=c("Dataset.x"="Dataset.Trt", "Dataset.y"="Dataset.Ctrl")) %>%
    filter((Subid.x != Subid.y)) %>%
    mutate(Overlap=ifelse(is.na(Overlap), 1, Overlap))
  
  return(Dmtx.long %>%
           mutate(Method=method))
}))

test <- Dmtxs %>%
  filter((Sex.x != Sex.y)) %>%
  group_by(Method) %>%
  mutate(Distance = (Distance - min(Distance))/(max(Distance) - min(Distance)))

test %>%
  filter(!(Method %in% c("Ranked", "Z-Score"))) %>%
  mutate(Overlap.bool=ifelse(Overlap == 1, "Within", "Between"), `Dataset Relationship`=factor(Overlap.bool)) %>%
  group_by(Method, Overlap.bool) %>%
  sample_n(5000) %>%
  group_by(Method) %>%
  sample_n(10000) %>%
  ggplot(aes(x=abs(Age.x - Age.y), y=Distance, color=`Dataset Relationship`)) +
  geom_jitter(width=.05, size=.2, alpha=.3) +
  scale_color_manual(values=c("Within"="blue", "Between"="red")) +
  facet_grid(Method~.) +
  xlab("|Age Difference|") +
  ylab("Normalized Distance") +
  scale_y_continuous(limits=c(0, 1), breaks=c(0, .2, .4, .6, .8, 1.0)) +
  theme_bw()
```

1274 x 770


## dMRI {.tabset}

```{r}
results <- readRDS('../data/dcorr/pdcorr_outputs_dMRI_AAL.rds')


continent <- c("IBATRT"="North America", "Utah1"="North America", "IPCAS_2"="Asia", "SWU1"="Asia", "UWM"="North America", "XHCUMS"="Asia", "SWU4"="Asia",
               "BNU2"="Asia", "IPCAS_3"="Asia", "SWU3"="Asia", "IPCAS_4"="Asia", "NYU2"="North America", "IPCAS_1"="Asia",
               "IPCAS_7"="Asia", "UPSM_1"="North America", "IACAS_1"="Asia", "IPCAS_5"="Asia", "NYU_1"="North America", "NYU_2"="North America", "BNU1"="Asia",
               "MRN1"="North America", "BNU3"="Asia", "HNU1"="Asia", "SWU2"="Asia", "IPCAS_8"="Asia", "JHNU"="Asia", "IPCAS_6"="Asia",
               "BMB1"="Europe")
results$Covariate$Continent <- continent[results$Covariate$Dataset]

dset.ord <- results$Covariate %>%
  select(Dataset, Continent, n, N) %>%
  distinct() %>%
  arrange(Continent, n) %>%
  mutate(id=row_number()) %>%
  mutate(Dataset.Newname=sub("_", "", Dataset))

results$Site <- results$Site %>%
  left_join(dset.ord %>% select(Dataset, Dataset.Newname), by=c("Dataset.Trt"="Dataset")) %>%
  mutate(Dataset.Trt=Dataset.Newname) %>% select(-Dataset.Newname) %>%
  left_join(dset.ord %>% select(Dataset, Dataset.Newname), by=c("Dataset.Ctrl"="Dataset")) %>%
  mutate(Dataset.Ctrl=Dataset.Newname) %>% select(-Dataset.Newname)

results$Covariate <- results$Covariate %>%
  left_join(dset.ord %>% select(Dataset, Dataset.Newname), by=c("Dataset"="Dataset")) %>%
  mutate(Dataset=factor(Dataset.Newname, levels=dset.ord$Dataset.Newname, ordered=TRUE)) %>% select(-Dataset.Newname)

results$Signal <- results$Signal %>%
  left_join(dset.ord %>% select(Dataset, Dataset.Newname), by=c("Dataset"="Dataset")) %>%
  mutate(Dataset=factor(Dataset.Newname, levels=dset.ord$Dataset.Newname, ordered=TRUE)) %>% select(-Dataset.Newname)

dset.ord <- dset.ord %>%
  select(-Dataset) %>%
  rename(Dataset=Dataset.Newname)
```

### Site Effects {.tabset}

```{r}
results$Site <- results$Site %>%
  ungroup() %>%
  mutate(p.value=p.adjust(p.value, method="BH"),
         Dataset.Trt=factor(Dataset.Trt, 
                            levels=(dset.ord %>% arrange(n, rev(as.character(Dataset))))$Dataset, 
                            ordered=TRUE),
         Dataset.Ctrl=factor(Dataset.Ctrl, 
                             levels=(dset.ord %>% arrange(n, rev(as.character(Dataset))))$Dataset, 
                             ordered=TRUE))
```

```{r, warning=FALSE, message=FALSE}
params <- list(Raw=list(method="Raw", title.hmap="Detectability of Site-Related Effect Before Site Correction"),
               ComBat=list(method="causal ComBat", title.hmap="Detectability of Site-Related Effect After ComBat"),
               ComBat=list(method="ComBat", title.hmap="Detetectability of Site-Related Effect After ComBat"),
               ZScore=list(method="Z-Score", title.hmap="Detectability of Site-Related Effect After Z-Scoring"))

plts <- lapply(params, function(param) {
  pval_hmap_chart(results$Site, method=param$method, title=param$title.hmap, preproc=FALSE)
})
names(plts) <- names(plts)
```

#### Raw

```{r, fig.height=5, fig.width=7, warning=FALSE, message=FALSE}
plot(plts$Raw)
```


#### ComBat

```{r, fig.height=5, fig.width=7, warning=FALSE, message=FALSE}
plot(plts$ComBat)
```

#### Ranked

```{r, fig.height=5, fig.width=7, warning=FALSE, message=FALSE}
plot(plts$Ranked)
```

#### Z-Score

```{r, fig.height=5, fig.width=7, warning=FALSE, message=FALSE}
plot(plts$ZScore)
```

### Between-Individual Covariate Effects {.tabset}

```{r}
results$Covariate <- results$Covariate %>%
  ungroup() %>%
  mutate(p.value=p.adjust(p.value, method="BH")) %>%
  filter(Variance > 0)
```

```{r}
tab.cov <- results$Covariate %>%
  group_by(Method, Effect.Name) %>%
  summarize(Sig=sum(p.value <= .05), N.Tests=n()) %>%
  mutate(Significant=sprintf("%d/%d", Sig, N.Tests)) %>%
  select(-c("Sig", "N.Tests")) %>%
  rename("Effect"=Effect.Name) %>%
  pivot_wider(Method, names_from="Effect", values_from="Significant") %>%
  select(Method, Sex, Age) %>%
  mutate(Method=factor(Method, levels=c("Raw", "ComBat", "Ranked", "Z-Score"),
                       ordered=TRUE)) %>%
  arrange(Method)
```

```{r}
tab.cov %>%
  kbl() %>%
  kable_paper("hover")
```


#### Forest Plot

```{r, fig.height=8, fig.width=6}
results$Covariate %>%
  mutate(Significant=ifelse(p.value <= .05, "Yes", "No"),
         Method=factor(Method, levels=c("Raw", "ComBat", "Ranked", "Z-Score"), ordered=TRUE),
         Dataset=factor(Dataset, levels=dset.ord$Dataset, ordered=TRUE),
         ypos= (as.numeric(Dataset) + (as.numeric(Method) - 2)/6)) %>%
  ggplot(aes(x=Effect, shape=Method, xmin=Effect.lwr.jk, xmax=Effect.upr.jk, y=ypos, 
             color=Significant)) +
    geom_pointrange() +
    facet_grid(".~Effect.Name") +
    geom_vline(aes(xintercept=0), color="black", linetype="dashed") +
    scale_color_manual(values=c("No"="red", "Yes"="darkgreen"), name="Significant") +
    scale_y_continuous(labels=dset.ord$Dataset, breaks=dset.ord$id,
                       limits=c(min(dset.ord$id) - .5, max(dset.ord$id) + .5), expand=c(0,0),
                       name="Dataset") +
    theme_bw() +
    ggtitle("Forest Plot")
```


#### Effects WRT Variability in the Data {.tabset}

##### Sex

```{r}
results$Covariate %>%
  filter(Effect.Name == "Sex") %>%
  pivot_longer(c("Entropy", "Variance"), names_to="Measure", values_to="Value") %>%
  ggplot(aes(x=Value, y=Effect, color=Dataset)) +
    geom_point() +
    facet_grid("Method~Measure", scales="free_x") +
    ylab("Sex Effect") +
    ggtitle("Sex Effect vs Notions of Variability in Sex Demographic") +
    theme_bw()
```

##### Age

```{r}
results$Covariate %>%
  filter(Effect.Name == "Age") %>%
  pivot_longer(c("Entropy", "Variance"), names_to="Measure", values_to="Value") %>%
  ggplot(aes(x=Value, y=Effect, color=Dataset)) +
    geom_point() +
    facet_grid("Method~Measure", scales="free_x") +
    ylab("Age Effect") +
    ggtitle("Age Effect vs Notions of Variability in Age Demographic") +
    theme_bw()
```

### Looking at Signal Preservation

```{r, fig.width=6, fig.height=3}
plt <- results$Signal %>%
  mutate(Measure=recode_factor(Community, "Homophilic"="Homophilic Difference", "Homotopic"="Homotopic Difference"),
         Method=factor(Method, ordered=TRUE, levels=c("Raw", "ComBat", "Z-Score", "Ranked"))) %>%
  ggplot(aes(p.value, color=Method)) +
  stat_ecdf(geom="step") +
    facet_grid(". ~ Measure") +
    scale_color_manual(values = c("Raw"="green", "ComBat"="darkgreen", "Z-Score"="red", "Ranked"="darkred")) +
    xlab("p-value") +
    ylab("ecdf of p-values") +
    geom_vline(xintercept = .05, linetype='dashed') +
    theme_bw() +
    ggtitle("Preservation of Signal Effect by Correction Technique") +
    geom_text(data=data.frame(x=.05, y=.8,Measure="Homophilic Difference", text="$\\alpha$=.05"),
            aes(x=x, y=y, label=TeX(text, output="character")), 
            nudge_x=.2, color='black', parse=TRUE)
as.ggplot(gtable_filter(ggplotGrob(plt), "axis-b-2", trim=FALSE, invert=TRUE))
```
